### 2024-03-07 Poster DPG/poster.tex
data
plots

poster

paper

Poster

\begin{minipage}{0.64\textwidth}
    \highlightOne{ Observables of excitations of interest } \\
    \begin{itemize}
        \item (CDW) Exciton: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} + g_{\vec{k}\downarrow} \right),\qquad g_{\vec{k}\sigma}$
        \item (AFM) Longitudinal magnon: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} - g_{\vec{k}\downarrow} \right)$
        \item (AFM) Transversal magnon: $1/N \sum_{k} \left( \tau_{\vec{k}} + \tau_{\vec{k}}^\dagger \right)$
        \item (SC) Amplitude (Higgs) mode: $1/N \sum_{k} \left( f_{\vec{k}} + f_{\vec{k}}^\dagger \right)$
        \item (SC) Phase (Anderson-Bogoliubov) mode: $\im /N \sum_{k} \left( f_{\vec{k}} - f_{\vec{k}}^\dagger \right) $
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}{0.35\textwidth}
\highlightOne{ Abbreviations }
\begin{equation*}
    \label{eqn:operators}
    \begin{aligned}
        n_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}\sigma}\,,          \\
        f_k     &\coloneqq  c_{-\vec{k}\downarrow} c_{\vec{k}\uparrow}\,, \\
        g_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}+\vec{Q}\sigma}\,,  \\
        \tau_k  &\coloneqq  c_{\vec{k}\uparrow}^\dagger c_{\vec{k}\downarrow}\,,
    \end{aligned}
\end{equation*}
\end{minipage}
}

@@

\posterbox{\boxmargin}{\dimexpr\firstbox + 53.2cm}{\boxwidth}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
{%
\highlightOne{ Key ideas }
\begin{itemize}
    \item Objective: capture collective excitations
\item Consider a time-dependent operator $\hat{a}(t) = \sum_j c_j(t) \hat{A}_j$ and the symplectic product $(\hat{A} | \hat{B}) \coloneqq \langle [\hat{A}^\dagger, \hat{B}] \rangle$
\item Write the Heisenberg EoM as matrix-vector EoM (w.r.t. to full interaction Hamiltonian)
\begin{equation*}
    \label{eqn:heisenberg}
    \begin{aligned}
        \ddt \hat{a}(t) = \sum_j \ddt c_j(t) \hat{A}_j &= \im \sum_j c_j(t) [H, \hat{A}_j] \\
        \Rightarrow \sum_j \underbrace{(\hat{A}_i | \hat{A}_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= \im \sum_j \underbrace{(\hat{A}_i | [\hat{H}, \hat{A}_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
        \Rightarrow \mN \ddt \vec{c}(t) &= \im \mM \vec{c}(t)\,.
    \end{aligned}
\end{equation*}
\item Generalized eigenvalue problem $\omega \mN \vec{v} = \mM \vec{v}$, real solutions if either $\mM$ or $\mN$ is nonnegative.
\begin{itemize}
    \item[$\rightarrow$] $\mM$ is nonnegative is thermal equilibrium
\end{itemize}
\end{itemize}

@@

\begin{minipage}{0.55\textwidth}
    \includegraphics[width=\textwidth]{plots/afm_cdw_peaks_overview.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the AFM and CDW spectral functions close to the phase transition.}}
\end{minipage}
\hfill
\begin{minipage}{0.44\textwidth}
    \begin{itemize}
        \item Orange region: System is in the CDW phase, blue region: System is in the AFM phase
        \item Peak position grows linearly with $U$ as the system moves away from the phase transition
        \item But it moves into the continuum (b) quadratically
        \item At the same time, the weights also vanish
    \end{itemize}
\end{minipage}
}

@@

\posterbox{\boxmargin}{109.7cm}{\boxwidth}{Possible outlook}
{%
\begin{itemize}
\item Incorporating phase-separated states into the mean-field theory
\begin{itemize}
    \item thereby providing deeper analysis of the negative $V$ regime of phase diagrams and collective excitations
\end{itemize}
\item Coupling the electronic system to the electromagnetic field to include the Anderson-Higgs mechanism for superconductors
\item Incorporating different fillings
\item Describing multi-band systems with even richer phases and collective excitations
\end{itemize}
}

>>>>

\begin{minipage}{0.64\textwidth}
    \highlightOne{ Observables of excitations of interest } \\
    \begin{itemize}
        \item (CDW) Exciton: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} + g_{\vec{k}\downarrow} \right)$
        \item (AFM) Longitudinal magnon: $1/N \sum_{k} \left( g_{\vec{k}\uparrow} - g_{\vec{k}\downarrow} \right)$
        \item (AFM) Transversal magnon: $1/N \sum_{k} \left( \tau_{\vec{k}} + \tau_{\vec{k}}^\dagger \right)$
        \item (SC) Amplitude (Higgs) mode: $1/N \sum_{k} \left( f_{\vec{k}} + f_{\vec{k}}^\dagger \right)$
        \item (SC) Phase (Anderson-Bogoliubov) mode: $\im /N \sum_{k} \left( f_{\vec{k}} - f_{\vec{k}}^\dagger \right) $
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}{0.35\textwidth}
\highlightOne{ Abbreviations }
\begin{equation*}
    \label{eqn:operators}
    \begin{aligned}
        n_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}\sigma} \\
        f_k     &\coloneqq  c_{-\vec{k}\downarrow} c_{\vec{k}\uparrow} \\
        g_{k\sigma} &\coloneqq  c_{\vec{k}\sigma}^\dagger c_{\vec{k}+\vec{Q}\sigma} \\
        \tau_k  &\coloneqq  c_{\vec{k}\uparrow}^\dagger c_{\vec{k}\downarrow}
    \end{aligned}
\end{equation*}
\end{minipage}
}

@@

\posterbox{\boxmargin}{\dimexpr\firstbox + 53.2cm}{\boxwidth}{Method: Iterated equations of motion (iEoM)}
{%
\highlightOne{ Key ideas \cite{Kalthoff17,Bleicker18}}
\begin{itemize}
    \item Objective: capture collective excitations
\item Consider a time-dependent operator $\hat{a}(t) = \sum_j c_j(t) \hat{A}_j$ and the symplectic product $(\hat{A} | \hat{B}) \coloneqq \langle [\hat{A}^\dagger, \hat{B}] \rangle$
\item Write the Heisenberg EoM as matrix-vector EoM (w.r.t. to full interaction Hamiltonian)
\begin{equation*}
    \label{eqn:heisenberg}
    \begin{aligned}
        \ddt \hat{a}(t) = \sum_j \ddt c_j(t) \hat{A}_j &= \im \sum_j c_j(t) [H, \hat{A}_j] \\
        \Rightarrow \sum_j \underbrace{(\hat{A}_i | \hat{A}_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= \im \sum_j \underbrace{(\hat{A}_i | [\hat{H}, \hat{A}_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
        \Rightarrow \mN \ddt \vec{c}(t) &= \im \mM \vec{c}(t)\,.
    \end{aligned}
\end{equation*}
\item Generalized eigenvalue problem $\omega \mN \vec{v} = \mM \vec{v}$, real solutions if either $\mM$ or $\mN$ is nonnegative.
\begin{itemize}
    \item[$\rightarrow$] $\mM$ is nonnegative is thermal equilibrium
\end{itemize}
\end{itemize}

@@

\begin{minipage}{0.55\textwidth}
    \includegraphics[width=\textwidth]{plots/afm_cdw_peaks_overview.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the AFM and CDW spectral functions close to the phase transition.}}
\end{minipage}
\hfill
\begin{minipage}{0.44\textwidth}
    \begin{itemize}
        \item Orange shading: System is in the CDW phase, green shading: System is in the AFM phase
        \item Peak position grows linearly with $U$ as the system moves away from the phase transition
        \item But it moves into the continuum (b) quadratically
        \item At the same time, the weights also vanish
    \end{itemize}
\end{minipage}
}

@@

\posterbox{\boxmargin}{109.77cm}{\boxwidth}{Possible outlook}
{%
\begin{itemize}
\item Incorporating phase-separated states into the mean-field theory
\begin{itemize}
    \item thereby providing deeper analysis of the negative $V$ regime of phase diagrams and collective excitations
\end{itemize}
\item Coupling the electronic system to the electromagnetic field to include the Anderson-Higgs mechanism for superconductors
\item Incorporating different fillings
\item Describing multi-band systems with even richer phases and collective excitations
\end{itemize}
}
